The Part-Time Parliament\hfill\insertframenumber/\inserttotalframenumber

### 2011-05-25 trunk/disciplinas/usi_algsem/paxosTalk/paxosTalk.tex
26 slides, 59 pages

@@

\vspace{2 mm}
\textbf{\textsc{Proof of Theorem}}.
\begin{itemize}
\item $B1(\beta \cup \{B'\})$ follows from $B1(\beta)$ and the fact that $B'_{bal} = b$, and the assumption about $b$.
\item $B2(\beta \cup \{B'\})$ follows from $B2(\beta)$ and the fact that $B'_{qrm} = Q$, and the assumption about $Q$.
\item For $B3(\beta \cup \{B'\})$, if \textit{MaxVote}$(b,Q,B) = -\infty$ then let $B'_{val}$ be any value; otherwise, let $B'_{val} = \text{\textit{MaxVote}}(b,Q,B)_{val}$. $B3(\beta \cup \{B'\})$ then follows from $B3(\beta)$. $\square$
\end{itemize} 
\end{frame}

@@

\vspace{4mm}
In the preliminary protocol, \textit{LastVote}$(b, v)$ represented a ``promise'' from $q$ not to vote in any ballot numbered $b' : \text{\textit{LastVote}}(b, v)_{bal} < b' < b$

\vspace{2mm}
Here, \textit{LastVote}$(b, v)$ represents a stronger ``promise'' from $q$ not to vote in any ballot numbered $b' < b$
% although this promise is stronger, it just representing not sending a LastVote(...) in cases the preliminary prot. would. 
% as seen, this doesn't affect consistency
% ANYway, this is arguable, as one could see that the collection of promises from the preliminary are equivalent to this
% one single promise.

@@

  \begin {itemize}
    \item A minimal execution of the basic protocol would take at most $5\Delta$
%     \begin {itemize}
%       \item the responses to message (1a) would arrive after $2\Delta$ (at most)
%       \item the responses to message (2a) would arrive after $2\Delta$ (at most)
%       \item the (3a) message would take at most $\Delta$
%     \end{itemize} 
    \vspace{2 mm}
    \item A leader would ensure progress, but that requires leader election     
    \begin {itemize}
      \item when a leader seems to have failed, a new one should be elected\\
      (the election takes time $T_{el}$)
      \item if not enough responses to (1a) or (2a) arrive after $2\Delta$, a ballot $B$ had started before $T_{el}$
      \begin{itemize}
        \item or too many failures or message losses occurred\ldots %which violates the assumptions for this protocol
      \end{itemize}
      %the other ballot may even have succeeded! 
      %maybe started by another process before T was fully elapsed
      \item in this case, a ballot with number $b' > B_{bal}$ may be started by the leader -- $NACK$s to (1a) or (2a) may have carried \bbal
      \item in the worst case, the leader receives a $NACK$ for (2a), $4\Delta$ after $T_{el}$
      \item as no other process initiated any ballot after $T_{el}$, the ballot numbered $b'$ would succeed $5\Delta$ after the $NACK$
    \end{itemize}
    \vspace{2 mm}
    \item The complete protocol, with leader election, terminates at most after $T_{el} + 9\Delta$
    \begin{itemize}
      \item if no message was lost, every correct process learns the decided value
    \end{itemize}

@@

  \begin{itemize}
    \item Each instance has an id $I_{id}$ -- and there should be a leader %although, as seen, that wouldn't be really necessary for consistency
    \item Phases (1a) and (1b) can be executed for many of them --
    e.g. $p$ sends $NextBallot(b,n)$, for all instances $I$ with $I_{id} > n$
    \item The response from $q$ (1b) would contain a $LastVote(I_{id}, b, v)$ message for each instance $I : I_{id} > n$ that $q$ voted in
    \item Another process can send $NextBallot(b',n')$, with $b' > b$,\\
    and $p$'s (2a) messages would be ignored from then on
    \item This brings the protocol latency, on most cases, down to $3\Delta$
    \begin{itemize}
      \item no leader changes, enough correct processes and enough messages
    \end{itemize}
    \item If each process sent messages (2b) to every other one, we'd have $2\Delta$ %show how this is done on the board
    \item If instance $I^A$ was passed (phase (3b) concluded) before $I^B$ had a value proposed (phase (2a)), then $I^A_{id} < I^B_{id}$
    % ORDERING PROPERTY
    % the leader needed to know the result of previous instances before starting a new one (= atomic broadcast)
  \end{itemize}

>>>>

  \pause

@@

\pause
\vspace{2 mm}
\textbf{\textsc{Proof of Theorem}}.
\begin{itemize}
\item $B1(\beta \cup \{B'\})$ follows from $B1(\beta)$ and the fact that $B'_{bal} = b$, and the assumption about $b$.
\item $B2(\beta \cup \{B'\})$ follows from $B2(\beta)$ and the fact that $B'_{qrm} = Q$, and the assumption about $Q$.
\item For $B3(\beta \cup \{B'\})$, if \textit{MaxVote}$(b,Q,B) = -\infty$ then let $B'_{val}$ be any value; otherwise, let $B'_{val} = \text{\textit{MaxVote}}(b,Q,B)_{val}$. $B3(\beta \cup \{B'\})$ then follows from $B3(\beta)$. $\square$
\end{itemize} 
\end{frame}

@@

%\vspace{4mm}
%In the preliminary protocol, \textit{LastVote}$(b, v)$ represented a ``promise'' from $q$ not to vote in any ballot numbered $b' : \text{\textit{LastVote}}(b, v)_{bal} < b' < b$

\vspace{4mm}
%Here, 
\textit{LastVote}$(b, v)$ represents a ``promise'' from $q$ not to vote in any ballot numbered $b' < b$
% although this promise is stronger, it just representing not sending a LastVote(...) in cases the preliminary prot. would. 
% as seen, this doesn't affect consistency
% ANYway, this is arguable, as one could see that the collection of promises from the preliminary are equivalent to this
% one single promise.

@@

  \begin {itemize}
    \item A minimal execution of the basic protocol would take at most $5\Delta$
%     \begin {itemize}
%       \item the responses to message (1a) would arrive after $2\Delta$ (at most)
%       \item the responses to message (2a) would arrive after $2\Delta$ (at most)
%       \item the (3a) message would take at most $\Delta$
%     \end{itemize} 
    \pause
    \vspace{2 mm}
    \item A leader would ensure progress, but that requires leader election     
    \begin {itemize}
      \item when a leader seems to have failed, a new one should be elected\\
      (the election takes time $T_{el}$)
      \item if not enough responses to (1a) or (2a) arrive after $2\Delta$, a ballot $B$ had started before $T_{el}$
      \begin{itemize}
        \item or too many failures or message losses occurred\ldots %which violates the assumptions for this protocol
      \end{itemize}
      %the other ballot may even have succeeded! 
      %maybe started by another process before T was fully elapsed
      \item in this case, a ballot with number $b' > B_{bal}$ may be started by the leader -- $NACK$s to (1a) or (2a) may have carried \bbal
      \item in the worst case, the leader receives a $NACK$ for (2a), $4\Delta$ after $T_{el}$
      \item as no other process initiated any ballot after $T_{el}$, the ballot numbered $b'$ would succeed $5\Delta$ after the $NACK$
    \end{itemize}
    \vspace{2 mm}
    \pause
    \item The complete protocol, with leader election, terminates at most after $T_{el} + 9\Delta$
    \begin{itemize}
      \item if a majority of processes didnt't fail during that time
      \item and if the leader didn't fail for $9\Delta$ after $T_{el}$
      \item and if enough messages were delivered
    \end{itemize}

@@

  \begin{itemize}
    \item Each instance has an id $I_{id}$ -- and there should be a leader %although, as seen, that wouldn't be really necessary for consistency

    \pause
    \item Phases (1a) and (1b) can be executed for many of them --
    e.g. $p$ sends $NextBallot(b,n)$, for all instances $I$ with $I_{id} > n$
    \item The response from $q$ (1b) would contain a $LastVote(I_{id}, b, v)$ message for each instance $I : I_{id} > n$ that $q$ voted in
    \item Another process can send $NextBallot(b',n')$, with $b' > b$,\\
    and $p$'s (2a) messages would be ignored from then on
    \item This brings the protocol latency, on most cases, down to $3\Delta$
    \begin{itemize}
      \item no leader changes, enough correct processes and enough messages
    \end{itemize}

    \pause
    \item If each process sent messages (2b) to every other one, we'd have $2\Delta$ %show how this is done on the board

    \pause
    \item If instance $I^A$ was passed (phase (3b) concluded) before $I^B$ had a value proposed (phase (2a)), then $I^A_{id} < I^B_{id}$
    % ORDERING PROPERTY
    % the leader needed to know the result of previous instances before starting a new one (= atomic broadcast)
  \end{itemize}
